\bf Title here

### 2020-09-06 paper/paper.Rmd
a quick change  by apply the most recent version of ferrn pacakge (color)

library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)
```

@@

```{r toy-pca, fig.height = 6, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
# holes_1d_geo %>% explore_proj_pca(col = info) 
# holes_1d_better%>% explore_proj_pca(col = info) 
# 
# bind_rows(holes_1d_geo, holes_1d_better) %>% explore_proj_pca(col = method)
# 
# 
# dt <- bind_rows(holes_1d_better, holes_1d_geo) %>% 
#   compute_pca() %>% 
#   `$`(combined)
# 
# last <- dt %>% 
#   filter(info == "interpolation") %>% 
#     group_by(method) %>% 
#   filter(id == max(id))
# 
# start <- dt %>% filter(id == 1)
# 
# dt %>% 
#   ggplot(aes(x = PC1, y = PC2, col = info)) + 
#   geom_point() + 
#   #facet_wrap(vars(method)) + 
#   theme(aspect.ratio = 1, legend.position = "bottom") + 
#   geom_point(data = last, size = 7) + 
#   geom_point(data = start, size = 7)
# 
# 
# bind_rows(holes_1d_better, holes_1d_geo) %>%
#   filter(info == "interpolation") %>%
#   group_by(method) %>%
#   mutate(id = row_number()) %>%
#   ggplot(aes(x = id, y = index_val, group = method, col = as.factor(tries))) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(vars(method), ncol = 2)
# 
# ######
# dt <- bind_rows(holes_2d_better, holes_2d_geo) %>% 
#   compute_pca() %>% 
#   `$`(combined)
# 
# last <- dt %>% 
#   filter(info == "interpolation") %>% 
#     group_by(method) %>% 
#   filter(id == max(id))
# 
# start <- dt %>% filter(id == 1)
# 
# dt %>% filter(!is.na(info)) %>% 
#   ggplot(aes(x = PC1, y = PC2, col = info)) + 
#   geom_point() + 
#   geom_point(data = last, size = 7) + 
#   geom_point(data = start, size = 7) + 
#   facet_wrap(vars(method)) + 
#   theme(aspect.ratio = 1, legend.position = "bottom")

#####
# theory <- matrix(c(0,0, 1,0,0,0, 0, 1, 0, 0,0,0), ncol = 2)
# index <- holes()
# index(as.matrix(data_mult) %*% theory)
# 
# 
# theory <-orthonormalise(matrix(c(0,0.2, 0.7,0,0,0, 0, 0.7, 0.2, 0,0,0), ncol = 2))
# theory 
# index <- holes()
# index(as.matrix(data_mult) %*% get_last_basis(holes_2d_better))

dt <- bind_rows(holes_2d_better %>% mutate(algo = "not satisfactory"), holes_2d_better_max_tries %>% mutate(algo = "satisfactory")) %>% mutate(info = ifelse(info == "start", "new_basis", info)) %>% 
  compute_pca() %>% 
  `$`(combined)
last <- dt %>% 
  filter(info == "interpolation") %>% 
  group_by(algo) %>% 
  filter(id == max(id))
start <- dt %>% filter(id == 1)
dt %>% filter(!is.na(info)) %>% 
  ggplot() + 
  geom_point(aes(x = PC1, y = PC2, col = info)) + 
  geom_point(data = last, aes(x = PC1, y = PC2, col = info), size = 7) + 
  geom_point(data = start,aes(x = PC1, y = PC2, col = info), size = 7) + 
  facet_wrap(vars(algo)) + 
  theme(aspect.ratio = 1, legend.position = "bottom")

# bind_rows(holes_2d_better, holes_2d_geo) %>% 
#   filter(info == "interpolation") %>% 
#   group_by(method) %>% 
#   mutate(id = row_number()) %>% 
#   ggplot(aes(x = id, y = index_val, group = method, col = as.factor(tries))) + 
#   geom_point() + 
#   geom_line() + 
#   facet_wrap(vars(method), ncol = 1)

#holes_2d_geo %>% explore_trace_interp()

#xxx the info level need to be reorder to show the start and directional search points better.
```

@@

p1 <- bind_rows(holes_2d_better, holes_2d_better_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("max.tries = 25")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("max.tries = 500")

(p1 | p2) &
  theme(legend.position = "none") 
```

@@

*Example: initial value for polishing alpha* `search_polish` is a brute-force algorithm that evaluate 1000 points in the neighbourhood at each loop. Setting an appropriate initial value for polish_alpha would avoid wasting search on large vector space that are not likely to produce higher index value. The default initial value for polishing step is 0.5 and we are interested in whether this is an appropriate initial value to use after `search_geodesic`. The problem is a 1D projection of the small dataset using `search_geodesic` and followed by `search_polish`. The top-left panel of Figure \ref{polish-alpha} displays all the projection bases on the first two principal components, coloured by the `polish_alpha`. We can observe that rather than concentrating on the ending basis from `search_geodesic` as what polishing step is designed, `search_polish` searches a much larger vector space, which is unnecessary. Thus a customised smaller initial value for `polish_alpha` would be ideal. One way to do this is to initialised `polish_alpha` as the projection distance between the last two target bases. The top-right panel of Figure \ref{polish-alpha} shows a more desirable concentrated searching space near the ending basis. Both specifications of initial value allow the searches to reach the same ending index values.

```{r polish-alpha, fig.cap = "\\label{polish-alpha}PCA plot of two different polish alpha initialisations. A default polish alpha = 0.5 searches a larger space that is unncessary while a small customised initial value of polish alpha will search near the ending basis. Both intialisations reach the same ending index values. "}
p1 <- bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>% 
  explore_proj_pca(col = as.factor(alpha))

p2 <- bind_rows(holes_1d_geo, holes_1d_geo_polish) %>% 
  explore_proj_pca(col = as.factor(alpha))

p3 <- bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>%
  explore_trace_interp(col = method) + ylim(0.75, 0.95)

p4 <- bind_rows(holes_1d_geo, holes_1d_geo_polish) %>% 
  explore_trace_interp(col = method) +  ylim(0.75, 0.95)

((p1 | p2) /(p3 | p4)) +  plot_layout(heights = c(2, 1)) & theme(legend.position = "none")

@@

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
colour <- RColorBrewer::brewer.pal(3, "Dark2")
p5 <- kol_cdf_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_cdf_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[1]) + ggtitle("search_better, seed 12345")

@@

```{r 1d-2var-explore-proj-pca, fig.cap = "\\label{1d-2var-explore-proj-pca} The projected projection basis using principal components. The bases from better1 and better2 only search a proportion of the searching space while better_random produces a more exhausive search. The large overlapping of better1 and better_random is explained by the fact that both algorithms finds x2 in the end."}
interp1 <- kol_cdf_1d_2var_better 
interp2 <- kol_cdf_1d_2var_better_2
interp3 <- kol_cdf_1d_2var_better_random

bind_rows(interp1, interp2, interp3) %>% 
  mutate(algorithm = c(rep("better1", nrow(interp1)), 
                       rep("better2", nrow(interp2)), 
                       rep("better_random", nrow(interp3))),
         algorithm = fct_relevel(algorithm, c("better1", "better2", "better_random"))) %>% 
  explore_proj_pca(col = algorithm) + 
  scale_colour_brewer(palette = "Dark2")

>>>>

library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)
library(tourr)
```

@@

```{r toy-pca, fig.height = 6, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
dt <- bind_rows(holes_2d_better %>% mutate(algo = "not satisfactory"), 
                holes_2d_better_max_tries %>% mutate(algo = "satisfactory")) %>% 
 bind_rows(holes_2d_theory %>% mutate(algo = "satisfactory")) %>% 
  bind_rows(holes_2d_theory %>% mutate(algo = "not satisfactory")) %>% 
  mutate(algo = fct_relevel(algo, c("satisfactory", "not satisfactory")))%>% 
  compute_pca() %>% 
  `$`(aug)

dt %>% explore_proj_pca(facet = algo, size = 7, alpha = 0.5)
#dt %>% explore_proj_pca(facet = algo, axis = 2)

@@

holes_2d_better %>% mutate(max_tries = 25) %>% 
  dplyr::bind_rows(holes_2d_better_max_tries %>% mutate(max_tries = 500)) %>% 
  explore_trace_interp(col = max_tries, facet = max_tries) + 
  theme(legend.position = "none")
```

@@

<!-- *Example: initial value for polishing alpha* `search_polish` is a brute-force algorithm that evaluate 1000 points in the neighbourhood at each loop. Setting an appropriate initial value for polish_alpha would avoid wasting search on large vector space that are not likely to produce higher index value. The default initial value for polishing step is 0.5 and we are interested in whether this is an appropriate initial value to use after `search_geodesic`. The problem is a 1D projection of the small dataset using `search_geodesic` and followed by `search_polish`. The top-left panel of Figure \ref{polish-alpha} displays all the projection bases on the first two principal components, coloured by the `polish_alpha`. We can observe that rather than concentrating on the ending basis from `search_geodesic` as what polishing step is designed, `search_polish` searches a much larger vector space, which is unnecessary. Thus a customised smaller initial value for `polish_alpha` would be ideal. One way to do this is to initialised `polish_alpha` as the projection distance between the last two target bases. The top-right panel of Figure \ref{polish-alpha} shows a more desirable concentrated searching space near the ending basis. Both specifications of initial value allow the searches to reach the same ending index values.  -->

<!-- ```{r polish-alpha, fig.cap = "\\label{polish-alpha}PCA plot of two different polish alpha initialisations. A default polish alpha = 0.5 searches a larger space that is unncessary while a small customised initial value of polish alpha will search near the ending basis. Both intialisations reach the same ending index values. "} -->
<!-- p1 <- bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>%  -->
<!--   explore_proj_pca(col = as.factor(alpha)) -->

<!-- p2 <- bind_rows(holes_1d_geo, holes_1d_geo_polish) %>%  -->
<!--   explore_proj_pca(col = as.factor(alpha)) -->

<!-- p3 <- bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>% -->
<!--   explore_trace_interp(col = method) + ylim(0.75, 0.95) -->

<!-- p4 <- bind_rows(holes_1d_geo, holes_1d_geo_polish) %>%  -->
<!--   explore_trace_interp(col = method) +  ylim(0.75, 0.95) -->

<!-- ((p1 | p2) /(p3 | p4)) +  plot_layout(heights = c(2, 1)) & theme(legend.position = "none")  -->

<!-- ``` -->

@@

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
colour <- ferrn::botanical_pal()(3)
p5 <- kol_cdf_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_cdf_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[1]) + ggtitle("search_better, seed 12345")

@@

<!-- ```{r 1d-2var-explore-proj-pca, fig.cap = "\\label{1d-2var-explore-proj-pca} The projected projection basis using principal components. The bases from better1 and better2 only search a proportion of the searching space while better_random produces a more exhausive search. The large overlapping of better1 and better_random is explained by the fact that both algorithms finds x2 in the end."} -->
<!-- interp1 <- kol_cdf_1d_2var_better  -->
<!-- interp2 <- kol_cdf_1d_2var_better_2 -->
<!-- interp3 <- kol_cdf_1d_2var_better_random  -->

<!-- dt <- bind_rows(interp1, interp2, interp3) %>%  -->
<!--   mutate(algorithm = c(rep("better 1", nrow(interp1)),  -->
<!--                        rep("better 2", nrow(interp2)),  -->
<!--                        rep("better random", nrow(interp3))), -->
<!--          algorithm = fct_relevel(algorithm, c("better 1", "better 2", "better random")))  -->

<!-- dt %>%  -->
<!--   explore_proj_pca(col = algorithm, alpha = 0.5) +  -->
<!--   scale_colour_manual(values = color(3))  -->
<!-- ``` -->

### 2020-09-06 paper/paper.tex
apply the botanical palette to plot construction
a quick change  by apply the most recent version of ferrn pacakge (color)

\hypertarget{a-problem-of-not-monotinic}{%
\subsection{A problem of not
monotinic}\label{a-problem-of-not-monotinic}}

@@

\emph{Example: initial value for polishing alpha}
\texttt{search\_polish} is a brute-force algorithm that evaluate 1000
points in the neighbourhood at each loop. Setting an appropriate initial
value for polish\_alpha would avoid wasting search on large vector space
that are not likely to produce higher index value. The default initial
value for polishing step is 0.5 and we are interested in whether this is
an appropriate initial value to use after \texttt{search\_geodesic}. The
problem is a 1D projection of the small dataset using
\texttt{search\_geodesic} and followed by \texttt{search\_polish}. The
top-left panel of Figure \ref{polish-alpha} displays all the projection
bases on the first two principal components, coloured by the
\texttt{polish\_alpha}. We can observe that rather than concentrating on
the ending basis from \texttt{search\_geodesic} as what polishing step
is designed, \texttt{search\_polish} searches a much larger vector
space, which is unnecessary. Thus a customised smaller initial value for
\texttt{polish\_alpha} would be ideal. One way to do this is to
initialised \texttt{polish\_alpha} as the projection distance between
the last two target bases. The top-right panel of Figure
\ref{polish-alpha} shows a more desirable concentrated searching space
near the ending basis. Both specifications of initial value allow the
searches to reach the same ending index values.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/polish-alpha-1.pdf}
\caption{\label{polish-alpha}PCA plot of two different polish alpha
initialisations. A default polish alpha = 0.5 searches a larger space
that is unncessary while a small customised initial value of polish
alpha will search near the ending basis. Both intialisations reach the
same ending index values.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/1d-2var-explore-proj-pca-1.pdf}
\caption{\label{1d-2var-explore-proj-pca} The projected projection basis
using principal components. The bases from better1 and better2 only
search a proportion of the searching space while better\_random produces
a more exhausive search. The large overlapping of better1 and
better\_random is explained by the fact that both algorithms finds x2 in
the end.}
\end{figure}

>>>>

\hypertarget{a-problem-of-not-monotonic}{%
\subsection{A problem of not
monotonic}\label{a-problem-of-not-monotonic}}

@@

@@
